---
title       : Coursera Assignment 2
subtitle    : June 23, 2014
author      : Jean M.
job         : Student
framework   : io2012   # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets    : [bootstrap, quiz, shiny, interactive]
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

---

## Introduction

```{r echo = F, message = F, cache = F}
opts_chunk$set(results = 'asis', comment = NA, message = F, tidy = F)
```
We developped an app plotting some of the probability density functions available in R.

The parameters necessary for each distribution adapt to the distribution chosen. \

For example, if you want to draw a normal curve, the app asks for mean and sd. I you wnat to draw a Poisson curve, it asks for lambda.

Densities are drawn by generating observations (x) and calculating the density (d- function in R). 
Cumulative densities curves work by providing the plot with a the p- function.

--- .class #id 

## Probability Density Functions

R pseudo and parameters:

    -     binom = size, prob
    -     chisq = df, ncp
    -     f     = df1, df2, ncp
    -     norm  = mean, sd
    -     hyper = m, n, k
    -     pois  = lambda
    -     t     = df, ncp
    -     unif  = min, max

---
## URL 

http://coursera.shinyapps.io/densities

The next 2 slides are trying some of slidify new functionalities.

---  &radio
## R Base

What is the base R function or operator that concatenate 2 character vectors?

1. +
2. _paste_
3. glue
4. stick
5. concatenate

*** .hint 
tooth

*** .explanation 
cpaste("abc","qwe",sep="")

--- &interactive
## Interactive Console

```{r opts.label = 'interactive', results = 'asis'}
require(googleVis)
M1 <- gvisMotionChart(Fruits, idvar = 'Fruit', timevar = 'Year')
print(M1, tag = 'chart')
```

